\documentclass[a0paper,landscape]{article}

% --- Geometry for A0 Poster ---
\usepackage[margin=4cm]{geometry}
\usepackage{multicol}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{bm}

% --- Custom Font Settings ---
\renewcommand{\familydefault}{\sfdefault} % Sans Serif for better poster readability

% --- Document Properties ---
\begin{document}
\pagestyle{empty}

% --- Header ---
\begin{center}
    {\fontsize{100}{120}\selectfont \bfseries Authorship Verification: Stylometric Pipelines vs. Transformer Ensembles} \\[2cm]
    {\fontsize{50}{60}\selectfont Group Members: [Student Name 1], [Student Name 2], [Student Name 3]} \\[1cm]
    {\fontsize{40}{50}\selectfont Department of Computer Science, [University Name]}
\end{center}

\vspace{3cm}
\noindent\rule{\textwidth}{10pt}
\vspace{3cm}

\begin{multicols}{3}
\raggedcolumns
\fontsize{30}{36}\selectfont

    % ── COLUMN 1: Introduction ──
    {\huge \bfseries 1. Problem Definition}
    \vspace{0.5cm}
    
    Authorship Verification (AV) is the task of determining whether two given texts $T_1$ and $T_2$ were written by the same author.
    \begin{itemize}
        \item \textbf{Input}: Pair of texts $(T_1, T_2)$.
        \item \textbf{Output}: Binary label $y \in \{0, 1\}$.
    \end{itemize}
    The challenge lies in capturing \textit{style} (writing fingerprints) rather than \textit{content} (topics).

    \vspace{2cm}

    {\huge \bfseries 2. Solution 1: Classical Stylometry}
    \vspace{0.5cm}

    Our first approach focuses on interpretable linguistic markers:
    \begin{itemize}
        \item \textbf{Lexical Richness}: Yule's K and Simpson's D indices.
        \item \textbf{Syntactic Patterns}: Function word frequency.
        \item \textbf{Classifier}: XGBoost trained on stylometric feature vectors.
    \end{itemize}
    \textit{Mathematical precision (Yule's K)}:
    \begin{equation}
        K = 10^4 \cdot \frac{\sum_{i=1}^\infty i^2 V_i - N}{N^2}
    \end{equation}

    \columnbreak

    % ── COLUMN 2: Deep Learning ──
    {\huge \bfseries 3. Transformer Ensemble Solution}
    \vspace{0.5cm}
    
    We implement a dual-paradigm ensemble:
    
    \textbf{A. DeBERTa-v3 Cross-Encoder}
    \begin{itemize}
        \item Fully captures token-level stylistic interactions.
        \item Input: $[CLS] T_1 [SEP] T_2 [SEP]$.
    \end{itemize}
    
    \textbf{B. Siamese MiniLM Bi-Encoder}
    \begin{itemize}
        \item Independent encoding of $T_1$ and $T_2$.
        \item Faster inference, captures global structural cues.
    \end{itemize}

    \vspace{2cm}

    {\huge \bfseries 4. Fusion: Weighted Soft-Voting}
    \vspace{0.5cm}

    Final prediction is a weighted sum of probabilities:
    \begin{equation}
        P_{ensemble} = \sum_{i=1}^n w_i \cdot \sigma(\text{logit}_i)
    \end{equation}
    where $w_{Big} = 0.5$, $w_{Small} = 0.1$, etc.

    \columnbreak

    % ── COLUMN 3: Results & Conclusion ──
    {\huge \bfseries 5. Results \& Evaluation}
    \vspace{0.5cm}

    Metric: \textbf{Macro F1 Score}
    \begin{center}
    \fontsize{25}{30}\selectfont
    \begin{tabular}{lc}
        \toprule
        \textbf{Model Configuration} & \textbf{Macro F1} \\ \midrule
        Classical ML (Stylometry) & 0.7521 \\
        Bi-Encoder (MiniLM) & 0.7734 \\
        Cross-Encoder (DeBERTa) & 0.7951 \\
        \textbf{Ensemble (Optimal)} & \textbf{0.8083} \\ \bottomrule
    \end{tabular}
    \end{center}
    The ensemble provides a \textbf{1.32\% boost} over the best single model.

    \vspace{2cm}

    {\huge \bfseries 6. Critical Insights}
    \vspace{0.5cm}

    \begin{itemize}
        \item \textbf{Robustness}: Broad diversity in the ensemble reduces variance on cross-domain pairs.
        \item \textbf{Efficiency}: The pipeline automatically utilizes Apple Silicon (MPS).
        \item \textbf{Improvement}: Adding MPNet-base to the ensemble could further boost performance.
    \end{itemize}

    \vspace{2cm}

    {\huge \bfseries 7. Conclusion}
    \vspace{0.5cm}

    By merging deep transformer-based interaction with localized stylometric features, we achieve a state-of-the-art balance of accuracy and generalization in Authorship Verification.

\end{multicols}

\end{document}
